Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2019-02-08 analysis/presentation/sim_survey_presentation.Rmd
Tweak presentation for MUN Biology seminar

---
title: "Using simulation to optimize the sampling design of fisheries-independent trawl surveys"
author: "Paul M. Regular & Fran Mowbray"
date: "September 12^th^, 2018"
output:
  ioslides_presentation:
    widescreen: true
    incremental: true
    logo: dfo_logo.png
    css: dfo_style.css
bibliography: references.bib
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      fig.width = 10, 
                      fig.height = 5.2)
knitr::opts_knit$set(root.dir = "../..")
```

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(crosstalk)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-09-04_test/test_output.RData")

@@

@@

- Conducted by many RFMOs
- Becoming increasingly important in stock assessment
- Very costly 💰
- General goal:
    - Maximize information & minimize expenses

@@

<dev class = "left">
```{r}
plot_trend(sim) %>% 
  tight_layout(yaxis = list(rangemode = "tozero"),
               margin = list(l = 70, r = 0, t = 0, b = 40, pad = 0))
```
</dev>

@@

<dev class = "left">
```{r}
plot_surface(sim) %>% tight_layout()
```
</dev>

@@

### Square grid with depth gradient

<dev class = "left">
```{r}
plot_ly(data = sim$grid_xy, x = ~x, y = ~y, color = ~depth, 
        symbol = I(15), size = I(4.5), name = "grid", type = "scatter", 
        text = ~depth) %>%
  colorbar(title = "Depth") %>%
  tight_layout(yaxis = list(title = "", scaleanchor = "x", zeroline = FALSE, 
                            showgrid = FALSE, showticklabels = FALSE,
                            tickcolor = "transparent"),
               xaxis = list(title = "", zeroline = FALSE, 
                            showgrid = FALSE, showticklabels = FALSE,
                            tickcolor = "transparent"))
```
</dev>

@@

<dev class = "left">
```{r}
plot_distribution_slider(sim, ages = 1:6, years = 1:6) %>% 
  tight_layout(margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

@@

<dev class = "left">
```{r}
plot_samp_dist(sim) %>% 
  tight_layout(margin = list(l = 0, r = 0, t = 0, b = 40, pad = 0))
```
</dev>

@@

<dev class = "left">
```{r}
plot_total_strat_fan(sim, surveys = 1:5, 
                     plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                     font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

@@

<dev class = "left">
```{r}
surveys <- sim$surveys[set_den %in% c(0.0005, 0.001, 0.002, 0.01) &
                         lengths_cap %in% c(10, 100, 500, 1000) &
                         ages_cap %in% c(5, 10, 50), ]
plot_age_strat_fan(sim, surveys = surveys$survey, 
                   years = 1:5, ages = sim$ages, select_by = "year",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

@@

<dev class = "left">
```{r}
plot_age_strat_fan(sim, surveys = surveys$survey, 
                   ages = 2:6, years = sim$years, select_by = "age",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

@@

<dev class = "left">
```{r}
slide_font <- list(size = 14, color = rgb(121, 121, 121, maxColorValue = 255))
surface_font <- list(titlefont = slide_font, 
                     tickfont = slide_font)
surface_scene <- list(
  xaxis = surface_font,
  yaxis = surface_font,
  zaxis = surface_font
)
plot_error_surface(sim, plot_by = "rule") %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

@@

<dev class = "left">
```{r}
plot_error_surface(sim, plot_by = "samples") %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

@@

<dev class = "left">
```{r}
main_sim <- sim
load("analysis/cod_sim_exports/2018-09-07_test/test_output.RData")
plot_age_strat_fan(sim, surveys = surveys$survey,
                   ages = 2:6, years = sim$years, select_by = "age",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

@@

## Code {.smaller}

### Population

```{r, echo = TRUE, eval = FALSE}

      set.seed(438)
      pop <- sim_abundance(ages = 1:20, years = 1:20,
                           R = sim_R(mean = 30000000, log_sd = 0.5,
                                     random_walk = TRUE),
                           Z = sim_Z(mean = 0.5, log_sd = 0.2,
                                     phi_age = 0.9, phi_year = 0.5)) %>%
        sim_distribution(grid = sim_grid(x_range = c(-140, 140), y_range = c(-140, 140),
                                         res = c(3.5, 3.5), shelf_depth = 200,
                                         shelf_width = 100, depth_range = c(0, 1000),
                                         n_div = 1, strat_breaks = seq(0, 1000, by = 20),
                                         strat_splits = 2),
                         ays_covar = sim_ays_covar(sd = 2.8, range = 300,
                                                   phi_age = 0.5, phi_year = 0.9,
                                                   group_ages = 5:20),
                         depth_par = sim_parabola(mu = 200, sigma = 70))

## Code {.smaller}

### Surveys

```{r, echo = TRUE, eval = FALSE}

      surveys <- expand_surveys(set_den = c(0.5, 1, 2, 5, 10) / 1000,
                                lengths_cap = c(5, 10, 20, 50, 100, 500, 1000),
                                ages_cap = c(2, 5, 10, 20, 50))
      sim <- test_surveys(pop,
                          surveys = surveys, n_sims = 5,
                          n_loops = 200, cores = 6,
                          q = sim_logistic(k = 2, x0 = 3),
                          growth = sim_vonB(Linf = 120, L0 = 5, K = 0.1, digits = 0),
                          export = "analysis/cod_sim_exports")

<!-- There is a conflict somewhere...had to contain plotly plots in a dev to get it working and I had to add a bunch of spaces to fudge centering in one of the tables -->

>>>>

---
title: "Using simulation to optimize the sampling design of fisheries-independent trawl surveys"
author: "Paul M. Regular & Fran Mowbray"
date: "2019-02-08"
output:
  ioslides_presentation:
    widescreen: true
    incremental: true
    logo: dfo_logo.png
    css: dfo_style.css
bibliography: references.bib
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      fig.width = 10, 
                      fig.height = 5.2)
knitr::opts_knit$set(root.dir = "../..")

```{r data, include = FALSE}

# xaringan::inf_mr()

library(SimSurvey)
library(plotly)
library(crosstalk)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-10-26_age_clust_test/test_output.RData")

@@

# N?

@@

- Conducted by many RFMOs
- Becoming increasingly important in stock assessment
- Very costly!
- General goal:
    - Maximize information & minimize expenses

@@

```{r}
plot_trend(sim) %>% 
  tight_layout(yaxis = list(rangemode = "tozero"),
               margin = list(l = 70, r = 0, t = 0, b = 40, pad = 0))
```

@@

```{r}
plot_surface(sim) %>% tight_layout(scene = list(xaxis = list(range = c(1, 10))))
```

@@

@@

```{r}
plot_distribution(sim, ages = 1:6, years = 1:6, type = "heatmap") %>% 
  tight_layout(margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```

@@

```{r}
plot_survey(sim) %>% 
  tight_layout(margin = list(l = 0, r = 0, t = 0, b = 40, pad = 0))
```

@@

```{r}
plot_total_strat_fan(sim, surveys = 1:5, 
                     plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                     font = list(size = 14, family = "'Montserrat', sans-serif"))
```

@@

```{r}
surveys <- sim$surveys[set_den %in% c(0.0005, 0.001, 0.002, 0.01) &
                         lengths_cap %in% c(10, 100, 500, 1000) &
                         ages_cap %in% c(5, 10, 50), ]
plot_age_strat_fan(sim, surveys = surveys$survey, 
                   years = 1:5, ages = sim$ages, select_by = "year",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```

@@

```{r}
plot_age_strat_fan(sim, surveys = surveys$survey, 
                   ages = 2:6, years = sim$years, select_by = "age",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```

@@

```{r}
slide_font <- list(size = 14, color = rgb(121, 121, 121, maxColorValue = 255))
surface_font <- list(titlefont = slide_font, 
                     tickfont = slide_font)
surface_scene <- list(
  xaxis = surface_font,
  yaxis = surface_font,
  zaxis = surface_font
)
plot_error_surface(sim, plot_by = "rule") %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```

@@

```{r}
plot_error_surface(sim, plot_by = "samples") %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```

@@

```{r}
main_sim <- sim
load("analysis/cod_sim_exports/2018-09-07_test/test_output.RData")
plot_age_strat_fan(sim, surveys = surveys$survey,
                   ages = 2:6, years = sim$years, select_by = "age",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```

@@
